Categorical Predictor Embeddings in Actuarial Modeling

### 2020-10-13 manuscript/manuscript.Rmd
more stuff in modeling section

## GLMs and Neural Networks

# A Minimalist Neural Network {#modelling}

@@

asdf

## Neural net

asdf

@@

asdf

>>>>

## Predictive Modeling with GLM and a Minimalist Neural Network

@@

We fit a GLM with the following specifications:

-   Target variable: Amount paid on building claim

-   Predictors: *Log* of **building insurance coverage**, **basement enclosure type**, **number of floors in the insured building**, *prefix* of **flood zone**, and ***primary residence***.

-   Link function: log

-   Distribution: gamma

We take the log of the continuous predictor **building insurance coverage** following (cite cas glm monograph), which allows the scale of the predictor to match that of the target variable. Because the **flood zone** variable in the original data contains 60 levels, we take the prefix of the zone code, which corresponds to the level of risk as determined by FEMA (source?). For example, *A01*, *A02*, and so on are recoded as simply *A*.

A log link together with the gamma distribution is a standard choice for severity modeling, which provides a multiplicative structure where the response is positive.

## A Simple Neural Network

(Note: this section is WIP doesn't match up w/ code, which is also WIP) For the neural net, we utilize the same responsible variable, amount paid on building claim. We normalize the numeric variable ***building insurance coverage***, one-hot encode the **primary residence** variable, and apply embedding layers of dimension one to the rest of the categorical variables. We then connect the embeddings and the normalized variable to a single output unit with softplus activation, where the softplus function is defined to be

\begin{equation}
x \mapsto \log(1 + e^x).
\end{equation}

Figure (todo: add figure) exhibits the architecture of our simple neural network.

@@

To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the root mean square error (RMSE) on the predicted and actual paid amounts.
